Merging Datasets Through Deep learning

### 2018-09-02 paper2018/triplet_selection.tex
adding minor changes

\subsection{Metric Based Triplet Selection}
Although the computation of there is $argmax^i \| x_{a} - x_{p}^i \|^2$ and $argmin^i \| x_{a} - x{_n}^i \|^2$ is infeasible because it involves quadratic comparisons within a dataset, we observe that the use of approximate nearest neighbor (ANN) indexes can actually make this problem tractable for the selection of triples.

Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.  They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.  Finding the nearest neighbors of a vector involves traversal of the tree to a leaf by evaluating the queried vector at each split point in the tree.  Depending on the position of the vector within the space bounded by a split point, it may need to traverse both points at a split node.  However, large portions of the tree (and hence most vectors in the dataset) never get compared to the queried vector.  The average complexity to query the vectors of a neighbor is $O(log N)$ where N is the number of vectors in the dataset.  Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.  In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.

@@

Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.  As in earlier work, selection of \textit{hard positives} is not really relevant because all positive data should be used to teach the network the right function.  Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.  There is no explicit attempt to filter out\textit{hard negatives} in the approach.  The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives for a join.  Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better discrimination for joins.  An ANN-based strategy also provides an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.

>>>>

\subsection{Metric Based Triplet Selection}
For the problem of joins, we ideally want the anchor and all of its positives to be clustered closest together and separated from the nearest negatives as clearly as possible.  Approximate nearest neighbor indexes are highly efficient methods for selecting the top-K neighbors of a given vector by Euclidean distance, cosine similarity or other distance metrics.  They are based on space partitioning algorithms, such as \textit{k-d trees}, where the vector space is iteratively bisected into two disjoint regions.  The average complexity to query the vectors of a neighbor is $O(log N)$ where N is the number of vectors in the dataset.  Implementations exist now for fast, memory-efficient ANN indexes that scale up to a billion vectors \cite{JDH17} using techniques to compress vectors in memory efficiently.  In our work, we used the Annoy ANN implementation \cite{annoy_git} in our work which is based on the refinements to \textit{k-d trees} ideas described in \cite{ann_paper}.

@@

Assuming one has the entire dataset indexed in an ANN index, the problem of triplet selection can be simplified by asking the ANN index for the top k-nearest neighbors of an \textit{anchor}, where k is given by the number of triplets that one desires to generate for each anchor.  As in earlier work, selection of \textit{hard positives} is not relevant because all positive data should be used to teach the network the right function.  Selection of negatives is the set of all nearest neighbors that are \textit{negatives}.  There is no explicit attempt to filter out\textit{hard negatives} in the approach.  The overall idea is that the set of negatives that appear in the nearest neighbor set at input are in fact the most important elements for the network to learn to discriminate from positives for a join.  Focusing on these elements, regardless of whether they are \textit{hard} or \textit{semi-hard} should lead to better discrimination for joins.  An ANN-based strategy also provides an important baseline to assess what if any learning was performed by the neural network in mapping input vectors to a different space.
